\ab{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations}

### 2021-03-18 papers/intro_paper/discussion.tex
changes in Sec. V

\ab{After testing our method to infer the QNM frequencies with GR and non-GR synthetic-signal 
injections in Gaussian noise, we have applied it to LIGO and Virgo real data. 
We have analysed GW events in O1, O2 and O3a (a total of 4 new events) that were not examined in Ref.~\cite{Abbott:2020jks} 
with the $\pSEOB$ model (see Table~\ref{tab:qnm_o1o2_results}). After combining our new 
results with the other GW events in O3a investigated with our method~\cite{Abbott:2020jks}, 
we have obtained more stringent bounds on the dominant QNM $(\ell=2,m=2)$.}

\ab{More specifically,} as expected, the event providing the best constraint
on the least-damped QNM to be date continues to be GW150914 [see
\eqref{GW150914_delta}]. In addition, even in the most agnostic and
conservative scenario where we combine the information from different
events using an hierarchical approach, at $90\%$ credibility, we
constrain the frequency of the least damped QNM to be within $\sim
9\%$ of the GR prediction -- an improvement of a factor of $\sim 4$
over the results reported in~\cite{Abbott:2020jks}. The constraints we
obtain on the frequencies and damping time of the least damped QNM are
compatible with the ones recently reported in
Ref.~\cite{Carullo:2021dui}, where measurements on QNMs were done
using only the post-merger part of the signal was analyzed.

>>>>

\ab{After testing our method to infer the QNM frequencies with GR and non-GR synthetic-signal 
injections in Gaussian noise, we have applied it to LIGO and Virgo real data. 
We have analyzed GW events in O1, O2 and O3a (a total of 4 new events) that were not examined in Ref.~\cite{Abbott:2020jks} 
with the $\pSEOB$ model (see Table~\ref{tab:qnm_o1o2_results}). After combining our new 
results with the other GW events in O3a investigated with our method~\cite{Abbott:2020jks}, 
we have obtained more stringent bounds on the dominant (or least-damped) QNM $(\ell=2,m=2)$.}

\ab{More specifically, as expected, the single GW event providing the best constraint
on the least-damped QNM to date continues to be GW150914 $(\df{220}=0.04^{+0.06}_{-0.04}, 
\dtau{220}=0.09^{+0.18}_{-0.18})$. In addition, in the most agnostic and
conservative scenario where we combine the information from different
events using a hierarchical approach~\cite{Zimmerman:2019wzo,Isi:2019asy}, we obtain 
at $90\%$ credibility $(\df{220}=0.02^{+0.09}_{-0.09}, \dtau{220}=0.13^{+0.42}_{-0.40})$. Thus, 
our results constrain the frequency (decay time) of the least damped QNM to be within $\sim
9\%$ ($\sim 40\%$) of the GR prediction --- an improvement of a factor of $\sim 4$ ($\sim 2$) 
over the results obtained with the $\pSEOB$ model in Ref.~\cite{Abbott:2020jks}.}

\ab{Furthermore, when assuming that the deviations from GR do not vary appreciably over the GW events 
that we have analyzed, and combine the likelihood functions, we have obtained the most stringent bounds  
on the dominant QNM $(\df{220}=0.02^{+0.03}_{-0.03}, \dtau{220}=0.11^{+0.12}_{-0.12})$. Those 
constraints are compatible, but sligthly better (especially for the decay time) that the ones recently reported in Ref.~\cite{Carullo:2021dui} 
(see first row in Table II therein), where measurements on QNMs were done using only the post-merger part of 
the signal, and included a larger set of GW events from O1, O2 and O3a.}
